\documentclass[11pt, a4paper]{article}
\usepackage[inner=1in,outer=1in,top=1in,bottom=1in]{geometry}
\pagestyle{empty}
\usepackage{placeins}
\usepackage{graphicx}
\usepackage{fancyhdr, lastpage, bbding, pmboxdraw}
\usepackage{amsmath, amssymb}
\usepackage[usenames,dvipsnames]{color}
\definecolor{darkblue}{rgb}{0,0,.6}
\definecolor{darkred}{rgb}{.7,0,0}
\definecolor{darkgreen}{rgb}{0,.6,0}
\definecolor{red}{rgb}{.98,0,0}
\usepackage[colorlinks,pdfusetitle,urlcolor=darkblue,citecolor=darkblue,linkcolor=darkred,bookmarksnumbered,plainpages=false]{hyperref}
%\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\pagestyle{fancyplain}
\fancyhf{}
\lhead{ \fancyplain{}{\CourseTitle} }
%\chead{ \fancyplain{}{} }
\rhead{ \fancyplain{}{\CourseSemester \CourseYear} }
%\rfoot{\fancyplain{}{page \thepage\ of \pageref{LastPage}}}
\fancyfoot[RO, LE] {page \thepage\ of \pageref{LastPage} }
\thispagestyle{plain}
\usepackage{tabularx}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{xspace}

\newcommand{\CourseNumber}{NPRE247}
\newcommand{\CourseTitle}{Modeling Nuclear Energy Systems\xspace}%
\newcommand{\CourseInstructor}{Prof. Kathryn Huff\xspace}%
\newcommand{\CourseSemester}{Fall\xspace}%
\newcommand{\CourseYear}{2018\xspace}%
\newcommand{\CourseDays}{MWF\xspace}%
\newcommand{\CourseStart}{10:00\xspace}%
\newcommand{\CourseEnd}{10:50\xspace}%
\newcommand{\CourseInstructorEmail}{kdhuff@illinois.edu}
\newcommand{\CourseRoom}{225A\xspace}%
\newcommand{\CourseBuilding}{Talbot Laboratory\xspace}%
\newcommand{\CourseUniversity}{University of Illinois, Urbana-Champaign\xspace}%
\newcommand{\TeachingAssistant}{Mohammad Mustafa\xspace}%
\newcommand{\TAOfficeHourDays}{Monday and Thursday \xspace}%
\newcommand{\TAOfficeHourStart}{1:00pm\xspace}%
\newcommand{\TAOfficeHourEnd}{1:50pm\xspace}%
\newcommand{\TAOfficeHourPlace}{the 220 Talbot Laboratory Student Lounge\xspace}
\newcommand{\CourseAssistants}{Zoe Richter and Tyler Kennelly\xspace}%
\newcommand{\CAOfficeHours}{Tu/Th 1-2pm and W/F 12-1pm \xspace}%
%\newcommand{\CAOfficeHourDays}{Tuesdays, Wednesdays, and Thursdays\xspace}%
%\newcommand{\CAOfficeHourStart}{1:00pm\xspace}%
%\newcommand{\CAOfficeHourEnd}{3:00pm\xspace}%
\newcommand{\CAOfficeHourPlace}{the 131 Talbot Laboratory Computer Lab\xspace}
\newcommand{\HuffOfficeHourDays}{Fridays\xspace}%
\newcommand{\HuffOfficeHourStart}{3:30pm\xspace}%
\newcommand{\HuffOfficeHourEnd}{4:30pm\xspace}%
\newcommand{\HuffOfficeHourPlace}{118 Talbot Laboratory, 104 S. Wright St.\xspace}
%\newcommand{\Course<++>}{<++>}
%\newcommand{\Course<++>}{<++>}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{\CourseNumber: \CourseTitle\\}
\author{\CourseUniversity}
\date{\CourseSemester \CourseYear}
\begin{document}
\maketitle
%\setlength{\unitlength}{1in}
\renewcommand{\arraystretch}{1.5}
\begin{center}
\begin{table}[h]
\begin{tabularx}{\textwidth}{rXrX}
\hline
\textbf{Instructor:} & \CourseInstructor & \textbf{Time:} & \CourseDays \CourseStart -- \CourseEnd \\
\textbf{Email:} &  \href{mailto:\CourseInstructorEmail}{\CourseInstructorEmail} & \textbf{Place:} & \CourseRoom \CourseBuilding\\
\hline
\end{tabularx}
\end{table}
\end{center}

\paragraph{Course Pages:}
\begin{enumerate}
        \item \url{https://mybinder.org/v2/gh/katyhuff/npre247/master}
        \item \url{https://compass2g.illinois.edu}
        \item \url{https://classroom.github.com}
        \item \url{https://github.com/katyhuff/npre247}
        \item \url{https://piazza.com/illinois/fall2018/\CourseNumber/home}
\end{enumerate}

\paragraph{TA Office Hours:} The teaching assistant for the course, 
\TeachingAssistant, will hold office hours \TAOfficeHourDays from 
\TAOfficeHourStart to \TAOfficeHourEnd in \TAOfficeHourPlace. 
Grade disputes will not be addressed in TA office hours. 

\paragraph{CA Office Hours:} The undergraduate course assistants for the course, 
\CourseAssistants, will hold office hours \CAOfficeHours in \CAOfficeHourPlace.
Grade disputes will not be addressed in CA office hours. 

\paragraph{Office Hours:} Prof. Huff will hold office hours by appointment only 
and will never be available for an appointment with less than 24 hours notice. 
Before making an appointment, please try the following options:
\begin{itemize}
\item If your colleagues might be helpful, please post your questions in the 
        forum provided for this purpose. 
\item If the TA or CAs might be helpful, please attend their office hours.
\item Email Prof. Huff. If possible, please phrase your question such that it 
        can be answered `Yes' or `No'.  Questions which require substantial 
        response should be asked during the lecture or office hours.
\end{itemize}

If none of the above are successful or appropriate, I am happpy to chat. 
Here's a url where you can pick a time and place that works for you: 
\href{http://katyhuff.youcanbook.me}{katyhuff.youcanbook.me}. It syncs with my 
calendar. Once you've filled it out, we'll both receive an email that confirms 
the details.

\paragraph{Main References:}
A few essential references for this course will be assigned as readings. The 
required text for this course is \cite{shultis_fundamentals_2016} while 
\cite{lamarsh_introduction_2017} is also recommended. For assistance in 
computational projects, \cite{scopatz_effective_2015} is available online and 
in the library as an ebook.

\bibliographystyle{unsrt}
\renewcommand{\refname}{\normalfont\selectfont\normalsize}\vspace{-1cm} 
\bibliography{bibliography}

\paragraph{Objectives:} 

This course will equip students to:

\begin{itemize}
\item Apply elementary nuclear physics to nuclear engineering. 
\item Classify and compare nuclear reactor materials and components.
\item Evaluate steady-state and transient operation of nuclear reactors.
\item Calculate aspects of nuclear energy removal and conversion.
\item Select and simulate radiation shielding.
\end{itemize}

\paragraph{Prerequisites:} 
\begin{itemize}
\item PHYS 212
\item MATH 285 (credit or concurrent registration)
\end{itemize}

\paragraph{Grading Policy:} Grades will be assigned as a weighted sum of the following work. 

\begin{table}[h]
\begin{tabularx}{\textwidth}{Xr}
\textbf{Work} & \textbf{Weight}\\
\hline
\textbf{Quizzes} & (10\%) \\
\textbf{Homework} & (15\%) \\
\textbf{Computer Projects} & (30\%) \\
\textbf{Midterm 1} & (15\%) \\
\textbf{Midterm 2} & (15\%) \\
\textbf{Final Exam} & (15\%) \\
\hline
\textbf{Total} & (100\%) \\
\end{tabularx}
\end{table}

\paragraph{Important Dates:}
\begin{center} \begin{minipage}{3.8in}
\begin{flushleft}
Midterm \#1       \dotfill September 26, 2018, 10:00am  \\
Midterm \#2       \dotfill October 31, 2018, 10:00am  \\
CP1 Deadline      \dotfill Month Date, Year, Time  \\
CP2 Deadline      \dotfill Month Date, Year, Time  \\
CP3 Deadline      \dotfill Month Date, Year, Time  \\
Final Exam        \dotfill December 17, 2018, 1:30pm-4:30pm  \\
\end{flushleft}
\end{minipage}
\end{center}

\paragraph{Class Policies:}  

\begin{itemize}
\item[] \textbf{Integrity:} This is an institution of higher
learning. You will be swiftly ejected from the course if you are caught
undermining its integrity. Note the
\href{http://www.provost.illinois.edu/academicintegrity/students.html}{Student's
Quick Reference Guide to Academic Integrity} and the
\href{http://studentcode.illinois.edu/article1_part4_1-401.html}{Academic
Integrity Policy and Procedure}.  
\item[] \textbf{Attendance:} Regular attendance is mandatory. Request approval for absence for extenuating circumstances prior to absence.
\item[] \textbf{Electronics:} Active participation is essential and expected. 
        Accordingly, students must turn off all electronic devices (laptop, 
        tablets, cellphones, etc.) during class. Exceptions may be granted for 
        laptops if engaging in computational exercises or taking notes. 
\item[] \textbf{Collaboration:} Collaboratively reviewing course materials and studying for exams with fellow students can be enriching.  This is recommended.  However, unless otherwise instructed, homework assignments are to be completed independently and materials submitted as homework should be the result of one's own independent work.
\item[] \textbf{Late Work:} Late work will not be accepted. Plan ahead. 
        An optional homework assignment and an optional quiz will each be 
        offered during Fall Break. These optional assignments can be completed to 
        replace your lowest grade in each category. This shall accomodate 
        unforseen circumstances and corresponding missed quizzes and homeworks.

\item[] \textbf{Make-up Work:} There will be no negotiation about late work 
        except in the case of absence documented by an absence letter from the 
        Dean of Students.  The university policy for requesting such a letter 
        is in 
        \href{http://studentcode.illinois.edu/article1_part5_1-501.html}{the 
        Student Code}. Please note that such a letter is appropriate for many 
        types of conflicts, but that religious conflicts require special early 
        handling. In accordance with university policy, students seeking an 
        excused absence for religious reasons should complete the 
	\href{http://odos.illinois.edu/community-of-care/resources/students/religious-observances/}{Request for Accommodation for Religious Observances Form} 
        The student should submit this
        form to the instructor and the Office of the Dean of Students by the end of the
        second week of the course to which it applies. 


\item[] \textbf{Grade Disputes:} It is important that you understand and agree 
        with the grade you receive on assignments and exams. If you would like 
        to dispute your score, you must send an explanation by email to Prof. 
        Huff within one week of recieving the grade.  
        \textbf{Do not expect us to regrade anything while in conversation with 
        you} as that would not be fair to the other students in the class, whose 
        homeworks were graded without them present.  If you request a regrade, 
        be aware that the entire assignment will be regraded and is subject to 
        double-jeopardy: it is possible that your score will go down.
        Regrade requests should be based on an error on our part (e.g., adding 
        up the points incorrectly) or what you suspect is a misunderstanding of 
        your work (e.g., arriving at the correct answer using an unexpected 
        technique). Regrade requests that argue with the rubric (e.g., ``this is 
        wrong, but you took too many points off'') will be returned without 
        consideration. 
        \textbf{Your work should stand alone.} If an assignment is disorganized or 
        ambiguous, and requires an extensive explanation to the grader, you 
        will likely still lose points. The homeworks not only evaluate your 
        understanding of the material - they also evaluate your ability to 
        communicate that understanding clearly and concisely.
\end{itemize}

\paragraph{Accessibility:} I hope that this course will be inclusive and 
accommodating for all learners. As such, I am committed upholding the vision 
and values of \href{http://www.inclusiveillinois.illinois.edu/index.html}{Inclusive Illinois}
in my 
classroom.  With regard to accommodating all learners, please note that many 
resources are provided through 
\href{http://disability.illinois.edu/academic-support/accommodations}{the 
Division of Disability Resources and Educational Services}.  To request 
particular accommodations, please contact me as soon as possible so that we can 
work out any necessary arrangements.

\paragraph{Safety:}
Emergencies can happen anywhere and at any time, so it’s important that we take 
a minute to prepare for a situation in which our safety could depend on our 
ability to react quickly. Take a moment to learn the different ways to leave 
this building. If there’s ever a fire alarm or something like that, you’ll know 
how to get out and you’ll be able to help others get out. Next, figure out the 
best place to go in case of severe weather - we’ll need to go to a low-level in 
the middle of the building, away from windows. And finally, if there’s ever 
someone trying to hurt us, our best option is to run out of the building. If we 
cannot do that safely, we’ll want to hide somewhere we can’t be seen, and we’ll 
have to lock or barricade the door if possible and be as quiet as we can. We 
will not leave that safe area until we get an Illini-Alert confirming that it’s 
safe to do so. If we can’t run or hide, we’ll fight back with whatever we can 
get our hands on. If you want to better prepare yourself for any of these 
situations, visit \url{police.illinois.edu/safe}. Remember you can sign up for 
emergency text messages at \url{emergency.illinois.edu}. This 
\href{http://police.illinois.edu/dpsapp/wp-content/uploads/2017/08/syllabus-attachment.pdf}{one-page-handout} 
discusses the Illinois Run-Hide-Fight strategy.


\paragraph{Other Resources:} 
University students typically experience a wide range of stressors during their 
time on campus. Accordingly, campus resources exist to help students manage  
stress levels, mental health, physical health, and emergencies while navigating 
this environment. I hope you will take advantage of these campus resources as 
soon as they can be of help.

\begin{itemize}
\item \href{https://campusrec.illinois.edu/}{The Campus Recreational Centers}
\item \href{http://counselingcenter.illinois.edu/}{The Counselling Center}
\item \href{http://www.mckinley.illinois.edu/clinics/mental\_health.htm}{The McKinley Mental Health Clinic}
\item \href{http://odos.illinois.edu/emergency/}{The Emergency Dean}
\end{itemize}

\pagebreak
\FloatBarrier
\renewcommand{\arraystretch}{1}
\begin{table}[h]
\begin{center}
\begin{tabular}{lllcccccc}
\multicolumn{8}{c}{\textbf{Course Schedule:}\textit{ Note that this schedule is 
subject to change.}}\\
&&&&&&&&\\
\textbf{Date} & \textbf{Week} & \textbf{Day} & \textbf{Unit} & \textbf{Chap.} & \textbf{Quiz}& \textbf{Date} & \textbf{HW} & \textbf{HW}\\
              &  &  &  &  & \textbf{Given} & \textbf{Due} & \textbf{Given} & \textbf{Due}\\ \hline
\hline
8/27 & 1 & M  & Intro &  & 1 &  & 1 & \\
8/29 & 1 & W & Fundamentals & 1 &  &  &  &  \\
8/31 & 1 & F & Fundamentals & 1 &  &  & 2 & 1 \\
9/3 & 2 & M & \textbf{Labor Day}  &  & 2 & 1 &  &  \\
9/5 & 2 & W & Modern Physics  & 2 &  &  &  &  \\
9/7 & 2 & F & Modern Physics & 2 &  &  & 3 & 2 \\
9/10 & 3 & M & Nuclear Models  & 3 & 3 & 2 &  &  \\
9/12 & 3 & W & Nuclear Energetics  & 4 &  &  &  &  \\
9/14 & 3 & F & Nuclear Energetics  & 4 &  &  & 4 & 3 \\
9/17 & 4 & M & Radioactivity  & 5 & 4 & 3 &  &  \\
9/19 & 4 & W & Radioactivity  & 5 &  &  &  &  \\
9/21 & 4 & F & Radioactivity  & 5 &  &  & 5 & 4 \\
9/24 & 5 & M & Review  &  & 5 & 4 &  &  \\
9/26 & 5 & W & Exam 1  &  &  &  &  &  \\
9/28 & 5 & F & Binary Nuc. Rxns.  & 6 &  &  & 6 & 5 \\
10/1 & 6 & M & Binary Nuc. Rxns.  & 6 & 6 & 5 &  &  \\
10/3 & 6 & W & Binary Nuc. Rxns.  & 6 &  &  &  &  \\
10/5 & 6 & F & Rad. Int. with Matter  &  &  &  & 7 & 6 \\
10/8 & 7 & M & Rad. int. with Matter & 7 & 7 & 6 &  &  \\
10/10 & 7 & W & Radiation Dosimetry  & 9 &  &  &  &  \\
10/12 & 7 & F & Radiation Dosimetry  & 9 &  &  & 8 & 7 \\
10/15 & 8 & M & Radiation Dosimetry  & 9 &  8 & 7 &  &  \\
10/17 & 8 & W & Neutron Balance  & 10 &  &  &  &  \\
10/19 & 8 & F & Criticality  & 10 &  &  & 9 & 8 \\
10/22 & 9 & M & Criticality  & 10 & 9 & 8 &  &  \\
10/24 & 9 & W & 6 Factor  & 10 &  &  &  &  \\
10/26 & 9 & F & 6 Factor  & 10 &  &  & 10 & 9 \\
10/29 & 10 & M & 6 Factor  & 10 & 10 & 9 &  & \\
10/31 & 10 & W & Exam 2  &  &  &  &  &  \\
11/2 & 10 & F & Reactor Materials   &  10   &    &    &  11  & 10  \\
11/5 & 11 & M & Reactivity Feedback & 10  & 11 & 10 &  &  \\
11/7 & 11 & W & Reactivity Feedback  & 10 &  &  &  &  \\
11/9 & 11 & F & Reactivity Feedback  & 10 &  &  & 12 & 11 \\
11/12 & 12 & M & Fission Prod. Poison & 10 & 12 & 11 &  &  \\
11/14 & 12 & W & Fisison Prod. Poison  & 10 &  &  &  &  \\
11/16 & 12 & F & Open &  &  &  &  $<13>$ & 12 \\
11/19 & 13 & M & \textbf{Fall Break}& & $<13>$ & 12 &  &  \\
11/21 & 13 & W & \textbf{Fall Break}  &  &  &  &  &  \\
11/23 & 13 & F & \textbf{Fall Break}  &  &  &  & 14 & $<13>$ \\
11/26 & 14 & M & Neutron Diffusion& 10 &14& $<13>$ &  & \\
11/28 & 14 & W & Neutron Diffusion  & 10 &  &  &  &  \\
11/30 & 14 & F & Neutron Diffusion  & 10  &  &  & 15 & 14 \\
12/3 & 15 & M & Neutron Diffusion & 10 & 15 & 14 &  &  \\
12/5 & 15 & W & Neutron Diffusion  &  10 &  &  &  &  \\
12/7 & 15 & F & Neutron Power & 11 &  &  &  & 15 \\
12/10 & 16 & M &  Nuclear Power& 11 &  & 15 &  &  \\
12/12 & 16 & W &  Ethics &  &  &  &  &  \\
12/14 & 16 & F & Review  &  &  &  &  &  \\
12/17 & 17 & M & \textbf{Final Exam} &   &  &  &  &  \\
\end{tabular}
\end{center}
\end{table}
\FloatBarrier



%%%%%% THE END 
\end{document} 
